Confocal Raman Thermometer for Microfluidic Devices

### 2018-11-26 paper.tex
Cambios de Martin

%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{gensymb}
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
}

@@

\begin{abstract}
\keywords{First keyword \and Second keyword \and More}
\end{abstract}

@@

Different techniques were develop to measure temperature inside microchannels. A common approach is to introduce in the flow a dye with a temperature dependent property \cite{dye1}\cite{dye2}. The measurement of this property with the proper calibration is used as a thermometer. This is an invasive method, with the disadvantage that the dye can interfere with the chemical reactions occurring in the channel or vice versa. This makes the method not useful for online monitoring.

Walrafen et al \cite{walrafen1} discovered that the infrared spectrum of water shows temperature dependent qualities and measured the existence of an isosbestic point around 3425~cm$^{-1}$. This molecular property can be sensed using Raman Scattering to get a temperature dependent signal that is intrinsic of water. This method was proposed and proved useful in microchannels \cite{raman1}\cite{raman2}\cite{raman3} where an epi-illumination microscope was adapted to measure Raman Scattering by exciting the water with a visible laser. As water absorption is low in the visible spectrum \cite{absorption} this method proved to be non-invasive. In this work we propose an improvement over these methods were spatial resolution is enhanced by using a confocal collection scheme. This is achieved by focusing the collected Raman signal in a optical fiber (instead of the traditional pinhole used in most confocal microscopes). Also, the use of a 405~nm excitation beam maximizes temperature signal as Raman emission increases strongly with frequency \cite{faris}, besides being a cheap wavelength. Finally, a dark field illumination scheme is used to get scattering or fluorescence images of the sample at the same time temperature measurements take place. This allowed to perform temperature maps that characterize the heat flow in the channel and the geometric and construction parameters that dominate heat dissipation.

@@

\begin{figure}[h!]\label{fig:setup}
\centering
\includegraphics[width=\columnwidth]{figs/setup.eps}
\caption{Schematic representation of the confocal microscope used for Raman thermometry of water. A 405~nm single mode fiber coupled laser is used as excitation beam. The beam is focused in the sample by using a 40X microscope objective which also collects the Raman emission. A dichroic mirror (420~LP) is used to separate the signal which is then focused on a multimode optical fiber to achieve confocal resolution. The other end of the fiber enters a specially designed spectrometer which divide the Raman spectrum in two detectors for later processing. A different wavelength (520 nm) is used to get a scattering image of the sample which is separated from the signal and the pump beam by means of a dichroic mirror (505~LP) and sent to a CMOS camera. Colored arrows indicate the wavelength and the propagation direction of each beam.}
\end{figure}

@@

To calibrate the method a temperature controlled water cell was used. This was constructed using a rectangular aluminum plate with a perforation sealed with two glass windows and containing around 150~$\mu$l of distilled water. A peltier cell was fixed at one side of the piece to achieve either heating or cooling and a thermistor is used to monitor the piece temperature.  Placing this cell in the sample plane of the microscope allows a temperature controlled water sample used to set the isosbestic point and to calibrate the method.

Aca iria un parrafo contando las caracteristicas de los microcanales que usamos como muestra (tal vez convenga pedirle a Martin que lo escriba o que nos diga que es relevante decir sobre el proceso con el que los armo). Cosas que pienso que van: que están pegados a cubres de 150 um. Que se uso KCl para setear la conductividad en 5000 mS/cm. Las medidas de los canales. Que se alimento con una fuente de tensión regulable de hasta 1kV logrando los campos eléctricos …

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/spectra.eps}
\label{fig:spectra}
\caption{Raman spectra of water at different temperatures. A dashed line marks the isosbestic point. At shorter wavelengths the signal decreases with rising temperature. At longer wavelengths the opposite behavior occurs. Shaded regions indicate the portion of the spectrum collected in each detector in the temperature measurements as shown in figure \ref{fig:setup}.}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/calib.eps}
\label{fig:calib}
\caption{Temperature signal $S$ as a function of the water sample temperature. A linear fit is used as calibration for the method. Dispersion around the linear fit gives a temperature resolution of $\Delta T = 0.8$ K.}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/temporal.eps}
\label{fig:temporal}
\caption{Temperature rise at turn on for a microchannel under elecroosmotic flow. Electric field is activated at $t=0$. Two different positions 5 mm apart show the same behavior. The position $x=0$ is set at the inlet reservoir. (Channel dimensions  b = 80~$\mathrm{\mu m}$, h = 100~$\mathrm{\mu m}$ and $L$ = 20~mm)}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/horizontal.eps}
\label{fig:horizontal}
\caption{Horizontal scan (perpendicular to the flow, parallel to the coverglass) showing a constant temperature rise across the channel (Channel dimensions  b = 80~$\mathrm{\mu m}$, h = 100~$\mathrm{\mu m}$ and $L$ = 40~mm).}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/vertical.eps}
\label{fig:vertical}
\caption{Two vertical scans at different dissipated powers in the same channel used in figure \ref{fig:horizontal}. Position zero corresponds to the center of the channel. On the right side lays the coverglass.}
\end{figure}

The final spatial scan is shown in figure \ref{fig:long} where a longitudinal scan was performed. Again, temperature shows a constant behavior along the channel, similar to what was shown in figure \ref{fig:temporal}. This is consistent with theoretical calculations \cite{jouleteorico} where temperature rise occurs in the very beginning of the channel and then a constant value is achieved. A simple calculation considering that all heat flows trough the floor of the channel (glass) can be useful to estimate the required temperature gradient needed to reach a stationary regime where the extracted heat compensates Joule effect. For a typical dissipated power of 40 mW and a channel of dimensions $b = h = 100$ $\mathrm{\mu m}$ and $L$ = 20~mm the required temperature difference between the ceiling and the floor is

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/long.eps}
\label{fig:long}
\caption{Longitudinal scan across a L = 20~mm channel. The experiment show a constant temperature rise around 13~K. }
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/rectas.eps}
\label{fig:rectas}
\caption{Temperature rise as a function of dissipated power per unit glass area on four different channel geometries. A linear fit is performed in each data set in order to compare the slope corresponding to each channel. The similarity between the lines seems to indicate that the glass floor of the channel dominates as dissipation mechanism.}
\end{figure}

>>>>

%
\RequirePackage{fix-cm}
%
%\documentclass{svjour3}                     % onecolumn (standard format)
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
\documentclass[twocolumn]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
\usepackage{gensymb}
\usepackage{xcolor}
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%
\begin{document}

@@

\institute{F. Author \at
              first address \\
              Tel.: +123-45-678910\\
              Fax: +123-45-678910\\
              \email{fauthor@example.com}           %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           S. Author \at
              second address
              \and
              Juan Martin Cabaleiro \at
           Laboratorio de Fluidodinámica, FIUBA, CONICET, Av. Paseo Colón 850, Buenos Aires, Argentina, and Laboratorio de Micro y Nanofluídica y Plasmas, UdeMM, Av. Rivadavia 2258, Buenos Aires, Argentina  \\
              Tel.: +54 11 5285 0467\\              
              \email{jmcabaleiro@gmail.com}  
}

@@

\begin{abstract}
\keywords{Raman thermometer \and electroosmotic flow \and spatial resolution}
\end{abstract}

@@

Typical characteristic dimensions in microfluidic devices are in the range $\sim10-100\, \mathrm{\mu m}$. In these devices it is generally necessary to either move the liquid or move species in solution from one point to another in the microfluidic network. To do so, one needs a pumping or species transport strategy. In many cases this is done via electroosmotic pumping or electrophoresis \cite{hunter2001,lyklema1995}. In any of these cases, an electric current is passed through the liquid, the applied power has to be dissipated. Depending on the device dissipation efficiency, the liquid temperature will rise more or less. In any case, as these devices are in often used in biological applications \cite{tian2008}, temperature is a critical parameter that has to be monitored and controlled. Moreover, even in non biological applications, the electroosmotic and electrophoretic mobility are a function of temperature \cite{tang2006} so that temperature rise may lead to unwanted pumping or electrophoretic behaviour. The readers are referred to the reviews by Xuan~\cite{xuan2008} and Cetin and Li~\cite{cetin2008} for a deeper description of joule heating in electrokinetic flows. 
Different techniques were developed to measure temperature inside microchannels. A common approach is to introduce in the flow a dye with a temperature dependent property~\cite{tang2006,ross2001,erickson2003,dye1,dye2}. The measurement of this property with the proper calibration is used as a thermometer. This is an invasive method, with the disadvantage that the dye can interfere with the chemical reactions occurring in the channel or vice versa. This makes the method not useful for online monitoring. Moreover, the measurement ``integrates'' the temperature in the channel height, not allowing for the measurement of temperature profiles normal to the channel bottom.

Walrafen et al \cite{walrafen1} discovered that the infrared spectrum of water shows temperature dependent qualities and measured the existence of an isosbestic point around 3425~$\mathrm{cm^{-1}}$. This molecular property can be sensed using Raman Scattering to get a temperature dependent signal that is intrinsic of water. This method was proposed and proved useful in microchannels \cite{raman1}\cite{raman2}\cite{raman3} where an epi-illumination microscope was adapted to measure Raman Scattering by exciting the water with a visible laser. As water absorption is low in the visible spectrum \cite{absorption} this method proved to be non-invasive. In this work we propose an improvement over these methods were spatial resolution is enhanced by using a confocal collection scheme. This is achieved by focusing the collected Raman signal in a optical fibre (instead of the traditional pinhole used in most confocal microscopes). Also, the use of a 405~nm excitation beam maximizes temperature signal as Raman emission increases strongly with frequency \cite{faris}, besides being a cheap wavelength. Finally, a dark field illumination scheme is used to get scattering or fluorescence images of the sample at the same time temperature measurements take place. This allowed to perform temperature maps that characterize the heat flow in the channel and the geometric and construction parameters that dominate heat dissipation. Our results show good agreement with those found in the literature.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/setup.eps}
\caption{Schematic representation of the confocal microscope used for Raman thermometry of water. A 405~nm single mode fiber coupled laser is used as excitation beam. The beam is focused in the sample by using a 40X microscope objective which also collects the Raman emission. A dichroic mirror (420~LP) is used to separate the signal which is then focused on a multimode optical fiber to achieve confocal resolution. The other end of the fiber enters a specially designed spectrometer which divide the Raman spectrum in two detectors for later processing. A different wavelength (520 nm) is used to get a scattering image of the sample which is separated from the signal and the pump beam by means of a dichroic mirror (505~LP) and sent to a CMOS camera. Colored arrows indicate the wavelength and the propagation direction of each beam.\label{fig:setup}}
\end{figure}

@@

To calibrate the method a temperature controlled water cell was used. This was constructed using a rectangular aluminum plate with a perforation sealed with two glass windows and containing around 150~$\mathrm{\mu l}$ of distilled water. A peltier cell was fixed at one side of the piece to achieve either heating or cooling and a thermistor is used to monitor the piece temperature.  Placing this cell in the sample plane of the microscope allows a temperature controlled water sample used to set the isosbestic point and to calibrate the method.

Microfluidics chips were made by polydimethylsiloxane (PDMS) replication of a Silicon-SU8 master~\cite{duffy1998rapid}. The PDMS microchannels produced were sealed with $150\,\mathrm{\mu m}$ thick glass coverslips. To improve the superficial bond between glass and PDMS, both parts were exposed to microwave air plasma and then gently held together. The plasma step is not mandatory due to the low manometric pressure into the channel, however plasma bonding allows for easier manipulation of the chip as the bonding is permanent. Plastic round reservoirs (made by cutting 10 ml plastic syringes, Diameter $\sim 16\,\mathrm{mm}$) were attached to both ends of the straight microchannels. We used 4 different channels whose dimensions are presented in table \ref{channeldims}.
\begin{table}[ht]
\small
  \caption{\ Dimensions of the channels used in this work}
  \begin{tabular*}{0.5\textwidth}{@{\extracolsep{\fill}}llll}
    %\hline 
    %..& & $\tau (\mathrm{s})$ &        
    \hline
    Channel & Width ($\mathrm{\mu m}$) & height ($\mathrm{\mu m}$) & length ($\mathrm{mm}$) \\
    \hline
    A & 50 & 100 & 20\\
    B & 80 & 100 & 10\\
    C & 80 & 100 & 20\\
    D & 80 & 100 & 40\\
    \hline
  \end{tabular*}
  \label{channeldims}
\end{table}

In this work we used a KCL solution with a conductivity of 5000 $\mathrm{\mu S/cm}$, and a regulated power source (up to 1 kV) to impose the external electric fields.

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/spectra.eps}
\caption{Raman spectra of water at different temperatures. A dashed line marks the isosbestic point. At shorter wavelengths the signal decreases with rising temperature. At longer wavelengths the opposite behavior occurs. Shaded regions indicate the portion of the spectrum collected in each detector in the temperature measurements as shown in figure \ref{fig:setup}.\label{fig:spectra}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/calib.eps}
\caption{Temperature signal $S$ as a function of the water sample temperature. A linear fit is used as calibration for the method. Dispersion around the linear fit gives a temperature resolution of $\Delta T = 0.8$ K.\label{fig:calib}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/temporal.eps}
\caption{Temperature rise at turn on for a microchannel under elecroosmotic flow. Electric field is activated at $t=0$. Two different positions 5 mm apart show the same behavior. The position $x=0$ is set at the inlet reservoir. (Channel dimensions  b = 80~$\mathrm{\mu m}$, h = 100~$\mathrm{\mu m}$ and $L$ = 20~mm).\label{fig:temporal}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/horizontal.eps}
\caption{Horizontal scan (perpendicular to the flow, parallel to the coverglass) showing a constant temperature rise across the channel (Channel dimensions  b = 80~$\mathrm{\mu m}$, h = 100~$\mathrm{\mu m}$ and $L$ = 40~mm).\label{fig:horizontal}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/vertical.eps}
\caption{Two vertical scans at different dissipated powers in the same channel used in figure \ref{fig:horizontal}. Position zero corresponds to the center of the channel. On the right side lays the coverglass.\label{fig:vertical}}
\end{figure}

The final spatial scan is shown in figure \ref{fig:long} where a longitudinal scan was performed. Again, temperature shows a constant behavior along the channel, similar to what was shown in figure \ref{fig:temporal}. This is consistent with theoretical and experimental results \cite{jouleteorico,xuan2008} where temperature rise occurs in the very beginning of the channel and then a constant value is achieved. A simple calculation considering that all heat flows trough the floor of the channel (glass) can be useful to estimate the required temperature gradient needed to reach a stationary regime where the extracted heat compensates Joule effect. For a typical dissipated power of 40 mW and a channel of dimensions $b = h = 100$ $\mathrm{\mu m}$ and $L$ = 20~mm the required temperature difference between the ceiling and the floor is

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/long.eps}
\caption{Longitudinal scan across a L = 20~mm channel. The experiment show a constant temperature rise around 13~K.\label{fig:long}}
\end{figure}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=\columnwidth]{figs/rectas.eps}
\caption{Temperature rise as a function of dissipated power per unit glass area on four different channel geometries. A linear fit is performed in each data set in order to compare the slope corresponding to each channel. The similarity between the lines seems to indicate that the glass floor of the channel dominates as dissipation mechanism.\label{fig:rectas}}
\end{figure}
